Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
fix bad refs/labels

	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
	\item Include explicit definitions for what we are assuming about a curve, i.e. smooth, projective, etc. Also, possibly discuss the relations to stacks, either here in or in the introduction. Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
	\item \begin{defn}
\label{}
If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
\end{defn}
\end{enumerate}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.  \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.  On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.  Maybe in a remark after the lemma?}
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}
\begin{proof}
By
Equation ~\ref{eqn:deg1_sat_ind_dim}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i = 1}^{r+ 1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$. By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$. Since $D$ is effective, the condition of equation ~\ref{eqn:deg1_sat_ind_dim} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.

@@

If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
then we may similarly apply Lemma ~\ref{g-0-admissible-cases} and
Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
\ldots, e_r)$ with relations generated up to degree $2e$.
 \end{proof}

@@

\label{}
Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring. Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.

@@

	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense. The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner. In particular, Lemma ~\ref{lem:raise-order-stacky} constructs generators with non-maximal pole orders at certain points, making the relations non-generic. 

@@

\label{}

@@

\label{}

>>>>

	\item Fix notation $\delta$ for $\deg \Delta$, $g$ for genus.
	\item While the remainder paper could be writen using stack-theoretic terms, as is done in \cite{vzb:stacky}, we shall adopt the simpler language of $\BQ$ divisors, thinking of $\sx$ as the underlying scheme $X$ with fractional points.
	\item Include explicit definitions for what we are assuming about a curve, i.e. smooth, projective, etc. Also, possibly discuss the relations to stacks, either here in or in the introduction. Make sure to make clear the assumption that we will work over an algebraically closed field through tensoring up.
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
	\item

	\begin{defn}
	\label{def:order-sup}
	If $z$ is a rational section of $\sco(D)$ denote the order of zero of $z$ at $P$ by $\ord_P^D(z)$.
	\item Define $(R_\halfcan)_d$ to refer to the $d^{th}$ component.
	\end{defn}
\end{enumerate}

@@

\begin{lem}
\label{lem:sat-1}
Let $X$ be a genus $g$ curve and $\halfcan' \in \di X \otimes \BQ$
satisfying $h^0(X, \lfloor{\halfcan'}\rfloor)\ge 1$. Suppose $P$ is not a base-point of $d\halfcan'$ for all $d\in \mathbb{N}$, meaning we can choose generators $u, x_1, \ldots, x_m$ of $R_{\halfcan'}$ in degree at most $\sigma$ for some $\sigma\in \mathbb{N}$, with $\deg u = 1$, $\ord_P^{\halfcan'}(x_i)=0$ for all $1 \leq i \leq m$, and $\ord_P^{\halfcan'}(u) = 0$.  Suppose $\halfcan = \halfcan' + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbb{N}$ such that
\begin{equation}
\label{eqn:deg1-sat-ind}
	h^0(X, \lfloor{d\halfcan}\rfloor) = h^0(X,\lfloor d\halfcan'
	\rfloor) + \left\lfloor d\frac{\alpha} {\beta} \right \rfloor \text{ for all } d \in \mathbb{
	N} \text{ such that } d \ge \frac{\beta}{\alpha},
\end{equation}
and let
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{\beta}
\]
be the positive best lower approximations of $\frac{\alpha}{\beta}$.
Then,

@@

\item[(c)] In particular, $R_\halfcan$ is generated over $R_\halfcan'$ in degrees at most $\beta$ with $I$ generated over $I'$ in degrees at most $\max(2\beta, \beta + \sigma)$.  \todo{Peter: Part (c) is immediate from (a) and (b), so maybe it shouldn't be its own section.  On the other hand, the other parts already have a lot of information written down (especial part (b)), so its not clear where it should be put.  Maybe in a remark after the lemma?}
%\item If $\gin_\prec(I')=\initial_\prec(I')$ then $\gin_\prec(I)=\initial_\prec(I)$.
%\item[(c)] A Gr\"{o}bner basis with the initial terms $y_i x_j$, $y_i y_j$,
%	and $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor
%	\frac{\alpha}{\beta} \rfloor} + 1}$ (really the subset of these with positive subscripts) as shown above minimally
%generates $I'$.
\end{enumerate}
\end{lem}
\begin{proof}
By
Equation ~\ref{eqn:deg1-sat-ind}, for any $d
\in \mathbb{N}$ such that $\lfloor d \frac{ \alpha}{\beta} \rfloor > 0$,

@@

%Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i = 1}^{r+ 1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$. By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$. Since $D$ is effective, the condition of equation ~\ref{eqn:deg1-sat-ind} is met, so by remark ~\ref{rem:deg1_sat_ind_gen_rel_degrees} of Lemma ~\ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.

@@

If $r \leq 5$ and $\sigma$ is not one of the exceptional cases,
then we may similarly apply Lemma ~\ref{lem:g-0-admissible-cases} and
Corollary ~\ref{cor:raise-stacky-order} to an appropriate base case
from Table ~\ref{table:g-0-base-cases} and deduce that $R(\sx,
\delta, \halfcan)$ is generated up  to degree $e := \max(5, e_1,
\ldots, e_r)$ with relations generated up to degree $2e$.
 \end{proof}

@@

\label{cor:main-refined}
Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring. Suppose Conjecture ~\ref{conj:relations-10}. Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.

@@

	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense. The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner. In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic. 

@@

\label{ques:generic-initial}

@@

\label{ques:algorithm}
